\documentclass[a4paper,12pt,titlepage]{scrreprt}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage[utf8x]{inputenc}
\usepackage{srcltx}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{picinpar}
\usepackage{verbatim}
\usepackage[english]{babel}
\usepackage{paralist}
\usepackage[avantgarde]{quotchap}
\usepackage[Sonny]{fncychap}
\usepackage[final]{pdfpages}
\usepackage{boxedminipage}
\usepackage{pifont}
\usepackage{tocbibind}
\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{url}
\usepackage{setspace}
\usepackage{caption}
\usepackage{bigstrut}
\usepackage{footnote}
\usepackage{wrapfig}
\usepackage{float}

\floatstyle{ruled}
\newfloat{code}{H}{lop}
\floatname{code}{Code}

\onehalfspacing
\captionsetup{tablename=Tab.}
\captionsetup{figurename=Fig.}
\setcounter{tocdepth}{3}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

\makesavenoteenv{itemize}

\begin{document}
\begin{titlepage}
\title{... cloud smth ...}
\author{P\u{a}ulesc Alin}
\date{July, 2012}

\begin{center}

    \textbf {\large West University of Timi\c{s}oara \\
	Faculty of Mathematics and Computer Science}\\[1.5cm]
    \textsc {\Large {Thesis}} \\[0.2cm]
    for the \\[0.2cm]
    \textsc {\Large {Bachelor's degree}}\\[0.2cm]
    \textsc {Department of Computer Science}\\[3cm]
    \textbf{\huge {... cloud smth ...}}\\[3cm]

    \begin{minipage}{0.4\textwidth}
        \begin{flushleft} \large
            \emph{Supervisor:}\\
	    Prof. Dr. Viorel \textsc{Negru}
        \end{flushleft}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \begin{flushright} \large
        \emph{Author:}\\
        \textsc{P\u{a}ulesc} Alin
        \end{flushright}
    \end{minipage}
    \null
    \vfill
    Timi\c{s}oara, July 2012
    \end{center}

\end{titlepage}


\pagenumbering{Roman}
\setcounter{secnumdepth}{-1}
\chapter{Acknowledgement}
\begin{center}
Hereby I express my gratitude to \emph{Prof. Dr. Viorel Negru}, my thesis supervisor,\\[0.2cm]
for his guidance and support and my \emph{family} who have made all this possible.
\end{center}

\chapter{Abstract}
  This paper aims to visit a long-held dream of computing as a utility, an old idea whose time has \emph{finally} come 
\emph{Cloud Computing}.\\[0.1cm]
\emph{Cloud Computing} is a new term for a dream which has recently become a commercial reality, cloud computing is
growing in a rapid step so developers should take it into account. 
The \emph{boom} in cloud computing over the last few years has led to a situation that is common to many innovations
and new technologies, many have heard of it, but few actually understand what it is and more importantly, 
how it can benefit them.\\
This paper will also try to approach problems like \emph{cloud monitoring}, how can one implement such a system, how others
already did it.

\setcounter{secnumdepth}{3}
\setcounter{chapter}{0}

\tableofcontents

\cleardoublepage

\pagenumbering{arabic}

\include{ch1Introduction}
\include{ch2Monitoring}
\include{ch3Eucalyptus}
\include{ch4Cloudkingdom}
\include{ch5Conclusions}
%\bibliographystyle{ieeetr}
%\bibliography{bibliography}
\end{document}
